Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-28 paper/main.tex
MOre fixes

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of participant-specific PPA ROIs.
        Light gray: The
        audio-description's field of view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across participants, we chose the same horizontal
        slice (x=-11) for all participants as this slice depicts voxels of
        significant clusters in almost all participants.
        The figure does not show voxels of the left cluster of the movie stimulus
        in sub-09 and sub-18, and voxels of the right cluster of the movie
        stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

\todo[inline]{SE: imo, key question is only partially answered: how close is
movie / audio to localizer". Can you corroborate figure 3 with some more
numbers? COH: schwierig vergleichbar (insb. unterschiedliche thresholds), daher
Bland-Altman-Plots -> as kinda mentioned in following paragraph}

>>>>

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of participant-specific PPA ROIs.
        Light gray: The
        audio-description's field of view \citep{hanke2014audiomovie}.
        To facilitate comparisons across participants, we chose the same horizontal
        slice (x=-11) for all participants as this slice depicts voxels of
        significant clusters in almost all participants.
        The figure does not show voxels of the left cluster of the movie stimulus
        in sub-09 and sub-18, and voxels of the right cluster of the movie
        stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}
